Model and results for identity signaling project

### 2020-06-24 paper/ms.tex

\documentclass[11pt,letterpaper]{article}
% \documentclass[11pt]{report}
% \documentclass{report}
% \documentclass{book}
\usepackage[bookmarks]{hyperref}
\usepackage{amssymb,amsmath}
% \usepackage{fullpage}
\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{float}
% \usepackage[margin=1.00in]{geometry}
\usepackage[margin=0.90in]{geometry}

@@

\vspace{1em}
\begin{table}[H]
  \centering
  \begin{tabular}{cp{3.5in}c}
    Symbol & Definition & Values tested (default in bold)  \\
    \toprule 
    $w$      & \emph{Homophily}, the ability of agents to preferentially interact with similar others & $\{0.0, 0.05, 0.10, \ldots, 0.5\}$ \\
    $d$      & \emph{Disliking penalty} imposed when one agent dislikes the other & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$ \\
    $\delta$ & Additional penalty when pair dislike one another & \textbf{0.25} \\
    $E_{cov}$ & \emph{Efficiency of covert signaling} & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$ \\
    $E_{ov}$ & \emph{Efficiency of overt signaling} & \textbf{0.5} \\
    $s$      & \emph{Similarity benefit} received by similar interacting pair & \textbf{??} \\
    $K$      & Number of agent identity traits & $\{\mathbf{3}, 9\}$ \\
    $S$      & Minimum fraction of traits in common for a pair to be considered similar & 
      $\{0.1, 0.2, \ldots, \mathbf{0.5}, \ldots, 1.0\}$\\
    $M$      & Number of traits used to define majority/minority populations & $\{\mathbf{2}, 4\}$\\
  \end{tabular}
  \caption{Global, as opposed to agent-specific, model parameters. 
  Explanatory model parameters are used to answer
  our guiding questions about identity communication strategies. In the final
  column the default value is in bold, if there is one. Homophily never has a
  default value because it is varied in every computational experiment
  condition we test.}
  \label{tab:params}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{cp{4.5in}}
    Agent property & Description \\
    \toprule
    $a_{ij}$   & Attitude of agent $i$ towards agent $j$; $a_i$ is the $N$-dimensional 
      attitude vector of agent $i$. \\
    $\tau_{ik}$ & Trait $k$ of agent $i$; $\tau_i$ is the $K$-dimensional trait vector of agent $i$. \\
    Signaling strategy & Either \emph{overt} or \emph{covert}. Overt signaling always
                         results in the communication of the signaler's traits,
                         while covert signalers only reveal their traits to 
                         ``similar'' others; dissimilar others do not receive a covert signal. \\
    Receiving strategy & Either \emph{churlish} or \emph{generous}. Churlish
                         receivers default to dislike other agents from whom they have
                         not received a signal. Generous receivers default to
                         a neutral attitude towards others from whom they have
                         not received a signal.
  \end{tabular}
  \caption{Agent attributes.}
  \label{tab:agentAttributes}
\end{table}

@@

Each trait $j$ of agent $i$ takes a value $\tau_{ik} \in \{-1, 1\}$. $-1$ and 1
are used only to emphasize that there are two opposing traits.
Attitudes are $a_{ij} \in \{-1, 0, 1\}$ with meanings of 
disliking, neutral, or liking. Attitudes are set at the signaling and receiving
rounds, explained in more detail below. Briefly, if agent $i$ recieves a
trait signal from agent $j$, $a_{ij}$ will be 1 if the two agents have
similar traits, and $-1$ if $i$ and $j$ are sufficiently different. Similarity
is $s_{ij} = 1 - d(\tau_i, \tau_j)$ where $d(\tau_i, \tau_j)$ is the
Hamming distance between trait vectors. The Hamming distance is the fraction
of vector elements that are different. So, if $\tau_i = (1,~-1,~1)$ and
$\tau_j = (1,~-1,~-1)$, then $d(\tau_i, \tau_j) = 1/3$ and $s_{ij}=2/3$.
Two agents are ``similar'' if their similarity $s_{ij} \geq S$, where
$S$ is the similarity threshold parameter. Otherwise they are considered
dissimilar.

If two agents are similar, this enables agents to like one another. On the
other hand, dissimilar agents may come to dislike one another if they signal
their traits to one another. As explained further in the following section on
model dynamics, inter-agent attitudes determine the probability agents will
interact; the payoff received when a particular dyad interacts; and the
probability that one agent chooses another as a teacher.

@@

At the signaling and receiving step, agents form attitudes about one another if
they receive a signal from

@@

The two agents interact with different probabilities
depending on their attitudes about one another, and depending on the 
assumed homophily level. If  Note that as $w \rightarrow 0.5$,
agents never interact with agents they dislike and always interact with 
agents they like.

\begin{equation}
  \Pr(\text{$i$ interacts with $j$}) = \frac{1 + w(a_{ij} + a_{ji})}{2}
\end{equation}
\noindent

@@

Payoffs are determined based on the similarity bonus, $s$, and the disliking
penalty $d$\footnote{In the SI we consider the case where the disliking penalty 
when both agents dislike each other is different from $d$. We call this $\delta$
and let it vary from 0 to $2d$}.

\begin{table}[h]
  \centering
  \begin{tabular}{cccc}
    Similar? & $a_{ij}$ & $a_{ji}$ & Payoff $\pi_i = \pi_j$ \\
    \toprule
    Yes   & 1 & 1   & $1 + s$ \\
    Yes   & 1 & 0   & $1 + s$ \\
    Yes   & 1 & -1  & $1 + s - d$ \\
    Yes   & 0 & 0   & $1 + s$ \\
    Yes   & -1 & 0  & $1 + s - d$ \\
    Yes   & -1 & -1 & $1 + s - 2d$ \\
    \midrule
    No    & 1 & -1  & $1 + s - d$ \\
    No    & 0 & 0   & $1$ \\
    No    & -1 & 0  & $1 - d$ \\
    No    & -1 & -1 & $1 - 2d$ \\
  \end{tabular}
  \caption{Interaction payoff matrix. Certain conditions are impossible, and so are not
  shown. For instance, it is necessary for two agents to be similar for 
  one agent to like another agent (i.e.\ have $a_{ij} = 1$). Note that
  due to churlish receiving, two agents may be similar, but one dislikes the
  other while the other likes the one. There could be agents who dislike one
  another due to churlish receiving if they have never signaled each other.}
\end{table}

@@

We are primarily interested in the prevalence of covert signaling at time
$t$. Usually, $t=T$, where $T$ is the number of iterations chosen for our 
computational experiments. The prevalence of overt signalers is the complement 
of the prevalence of covert signalers. One important result shows that the
prevalence of covert signalers at $t=T$ is positively correlated with the
prevalence of generous receivers at $t=T$.

\begin{table}[H]
  \centering
  \begin{tabular}{rp{3in}} %p{5in}}
    Symbol & Measure \\ %& Description \\
    \toprule
      $\rho_{cov}$ & Prevalence of covert signalers\\
    $1 - \rho_{cov} = \rho_{ov}$ & Prevalence of overt signalers  \\
     $\rho_{gen}$ & Prevalence of generous receivers \\
    $1 - \rho_{gen} = \rho_{ch}$ & Prevalence of churlish receivers \\
    $\rho_s^{minor}$, $\rho_s^{maj}$ & Prevalence of strategy $s \in \{cov, ov, gen, ch\}$ amongst minority/majority \\
    $\Pr(\text{$s$ invades})$ & Probability strategy $s \in \{cov, ov, gen, ch\}$ invades 
  \end{tabular}
  \caption{Summary of outcome measures. To indicate any of these values at
  a particular time, we add an additional subscript. For example, $\rho_{cov,t}^{maj}$
  is the prevalence of covert signalers among the majority at time $t$.}
  \label{tab:outcomeMeasures}
\end{table}

@@

This basic design initializes $N$ agents with a arndomized trait vector, 
an attitude vector, and a signaling and receiving strategy.
Randomly setting agent attributes means
choosing $\pm 1$ for each element of agent trait vectors with equal 
probabilities, and choosing a signaling and receiving strategy at random
with equal probabilities for each strategy type. Attributes are initialized
according to the agent's receiving strategy. Generous agents have all 
attitudes about other agents set to 0, indicating neutrality. Churlish agents
have all attitudes set to -1, since these agents dislike others by default.
This and all experiments iterate the model $T$ times, which
means $T$ signaling rounds, with $I$ interactions between signaling rounds,
and social learning after the signaling rounds. In this basic experiment,
we analyze the global prevalence of covert signalers at time $T$ ($\rho_{cov,T}$)
and the global prevalence of generous receivers at time $T$ ($\rho_{gen,T}$),
including calculating correlation between the two.

\subsubsection{Covert signaling in minority/majority populations}
The first variation on this basic model is intended to test our 
hypothesis that covert signaling prevalence in 
minority populations ($\rho_{cov}^{minor}$) is inversely correlated with
homophily. For this, we initialize the first $M$ traits out of $K$ to mark the 
minority and majority populations. The minority population has its first
$M$ trait vector elements set to $+1$ and the majority population has its
first $M$ trait vector elements set to $-1$. For example, if $K=5$, $M=2$,
and agent $i$ is in the minority, then its trait vector would be
$\tau_i = (-1, -1, -1, \pm 1, \pm 1)$; if $i$ is in the majority, its 
trait vector would be $\tau_i = (1, 1, 1, \pm 1, \pm 1)$, where in the last
two positions the value is chosen randomly with equal probabilities.
In this experiment we analyze the prevalence of covert signalers and 
generous receivers in the minority and majority populations at time T: 
$\rho_{cov,T}^{minor}$, $\rho_{cov,T}^{major}$,
$\rho_{gen,T}^{minor}$, and $\rho_{gen,T}^{major}$.

@@

\subsection{Evolution of covert signaling...}

\subsubsection{...under various homophily and disliking scenarios}

Here I co-vary the disliking penalties, which I set equal ($d=\delta$), and
homophily, $w$. Here, $r=0.25$ and $R=0.5$.

Specifically, I vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
As in the above experiment, I set $w \in \{0.0, 0.5, \ldots, 0.45\}$.

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/basic_disliking_signaling.pdf}
    \caption{Density of covert signalers.}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/basic_disliking_receiving.pdf}
    \caption{Density of churlish receivers.}
  \end{subfigure}

  \caption{Density of covert signalers and churlish receivers at $t=500$, 
    the final timestep.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}

\subsubsection{...as a function of covert signaling efficiency}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/basic_receptivity_signaling.pdf}
    \caption{Density of covert signalers.}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/basic_receptivity_receiving.pdf}
    \caption{Density of churlish receivers.}
  \end{subfigure}

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/receptivity_allcombos_reg.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/disliking_allcombos_reg.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Correlation between proportion of covert signalers and proportion of
    churlish receivers for all tested parameter combinations in both 
    receptivity (a) and disliking (b) experiments. (NEED TO CHECK HOW I'M AVERAGING
    HERE AND POSSIBLY AGGREGATE FURTHER AS A SMOOTHING FILTER. ALSO NEED TO
    )}
  \label{fig:regressions}
\end{figure}

\subsection{Minority-majority dynamics}

@@

We primarily vary the minority prevalence, $\rho^{minor}$, and set $M=1$ and
$K=3$, except for one heatmap in 
Figure~\ref{fig:covert-signaling-minority-heatmap}.

@@

\subsubsection{Minority covert signaling over homophily and disliking}

@@

In this experiment we begin with initial proportions, $\rho$ of one of the strategies
at 0.05 and consider this the ``invading'' strategy. $\rho_{cov,0}$ represents
the initial covert proportion, $\rho_{ov,0}$ the initial overt proportion,
$\rho_{ch,0}$ the initial churlish proportion, and $\rho_{gen,0}$ the 
initial generous proportion. We measure how often
a non-zero proportion of agents with the invading strategy manage to 
establish a permanent population, which we call invasion success. We calculated
invasion success for a number of experimental parameter settings, covarying
over disliking penalty ($d=\delta$) and homophily ($w$) in the first case,
and over relative covert receptivity ($r/R$) and homophily ($w$) 
in the second case (Figures~\ref{fig:cov-ov-invade} and~\ref{fig:ch-gen-invade}).

>>>>

\documentclass[11pt,letterpaper]{article}
% \documentclass[11pt]{report}
% \documentclass{report}
% \documentclass{book}
\usepackage[bookmarks]{hyperref}
\usepackage{amssymb,amsmath}
% \usepackage{fullpage}
\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{float}
% \usepackage[margin=1.00in]{geometry}
\usepackage[margin=0.90in]{geometry}

@@

\vspace{1em}
\begin{table}[H]
  \centering
  \begin{tabular}{cp{3.5in}c}
    Symbol & Definition & Values tested (default in bold)  \\
    \toprule 
    $w$      & \emph{Homophily}, the ability of agents to preferentially interact with similar others & $\{0.0, 0.05, 0.10, \ldots, 0.5\}$ \\
    $d$      & \emph{Disliking penalty} imposed when one agent dislikes the other & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$ \\
    $\delta$ & Additional penalty when pair dislike one another & \textbf{0.25} \\
    $E_{cov}$ & \emph{Efficiency of covert signaling} & $\{0.0, 0.05, 0.1,\ldots \mathbf{0.25}, \ldots, 0.5\}$ \\
    $E_{ov}$ & \emph{Efficiency of overt signaling} & \textbf{0.5} \\
    $s$      & \emph{Similarity benefit} received by similar interacting pair & \textbf{0.25} \\
    $K$      & Number of agent identity traits & $\{\mathbf{3}, 9\}$ \\
    $S$      & Minimum fraction of traits in common for a pair to be considered similar & 
      $\{0.1, 0.2, \ldots, \mathbf{0.5}, \ldots, 1.0\}$\\
    $M$      & \emph{Number of minority/majority traits} used to define majority/minority populations & $\{\mathbf{2}, 4\}$\\
    $R$      & \emph{Number of interaction rounds} following a signaling round \\
    $\alpha$ & Threshold payoff multiplier to give learner 50\% chance of 
               adopting teacher's strategy \\
    $\beta$  & Factor that, as it increases, both lowers chance of learner 
               adopting strategy when $\pi_{teach}/\pi_{learn} < \alpha$ and
               raises chance of learner adopting teacher strategy when 
               $\pi_{teach}/\pi_{learn} > \alpha$.
  \end{tabular}
  \caption{Global, as opposed to agent-specific, model parameters. 
  Explanatory model parameters are used to answer
  our guiding questions about identity communication strategies. In the final
  column the default value is in bold, if there is one. Homophily never has a
  default value because it is varied in every computational experiment
  condition we test.}
  \label{tab:params}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{cp{4.5in}}
    Agent property & Description \\
    \toprule
    $a_{ij}$   & Attitude of agent $i$ towards agent $j$; $a_i$ is the $N$-dimensional 
      attitude vector of agent $i$. \\
    $\tau_{ik}$ & Trait $k$ of agent $i$; $\tau_i$ is the $K$-dimensional trait vector of agent $i$. \\
    $s_{ij}$   & \emph{Similarity} between agents $i$ and $j$. Equal to $1-h(\tau_i,\tau_j)$ 
                 where $h(\tau_i, \tau_j)$ is the Hamming distance between 
                 $i$ and $j$'s trait vectors. \\ 
    Signaling strategy & Either \emph{overt} or \emph{covert}. Overt signaling always
                         results in the communication of the signaler's traits,
                         while covert signalers only reveal their traits to 
                         ``similar'' others; dissimilar others do not receive a covert signal. \\
    Receiving strategy & Either \emph{churlish} or \emph{generous}. Churlish
                         receivers default to dislike other agents from whom they have
                         not received a signal. Generous receivers default to
                         a neutral attitude towards others from whom they have
                         not received a signal.
  \end{tabular}
  \caption{Agent and inter-agent attributes.}
  \label{tab:agentAttributes}
\end{table}

@@

Each trait $j$ of agent $i$ takes a value $\tau_{ik} \in \{-1, 1\}$. $-1$ and 1
are used only to emphasize that there are two opposing traits.
Attitudes are $a_{ij} \in \{-1, 0, 1\}$ with meanings of 
disliking, neutral, or liking. Attitudes are set at the signaling and receiving
rounds, explained in more detail below. Briefly, if agent $i$ recieves a
trait signal from agent $j$, $a_{ij}$ will be 1 if the two agents have
similar traits, and $-1$ if $i$ and $j$ are sufficiently different. Similarity
is

\begin{equation}
  s_{ij} = 1 - h(\tau_i, \tau_j)
  \label{eq:similarity}
\end{equation}
\noindent
where $h(\tau_i, \tau_j)$ is the
Hamming distance between trait vectors. The Hamming distance is the fraction
of vector elements that are different. So, if $\tau_i = (1,~-1,~1)$ and
$\tau_j = (1,~-1,~-1)$, then $d(\tau_i, \tau_j) = 1/3$ and $s_{ij}=2/3$.
Two agents are ``similar'' if their similarity $s_{ij} \geq S$, where
$S$ is the similarity threshold parameter. Otherwise they are considered
dissimilar.

If two agents are similar, this enables agents to like one another. On the
other hand, dissimilar agents may come to dislike one another if they signal
their traits to one another. As explained further in the following section on
model dynamics, inter-agent attitudes determine the probability agents will
interact; the payoff received when a particular dyad interacts; and the
probability that one agent chooses another as a teacher. Dyad similarity 
also determines whether or not a covert signal is ``understood'' by a 
receiver who is not sufficiently similar to the sender. In this case, the
receiver's attitude about the sender will remain unchanged from its
initialization: $-1$ if the receiver is churlish and $0$ if the receiver is
generous.

@@

At the signaling and receiving step, an agent updates its attitude about another
agent if they receive a signal from that agent. How many agents receive a
single agent's signal depends on whether the signaling agent is an overt or
covert signaler, and the global parameters \emph{efficiency of overt signaling}, $E_{ov}$,
and \emph{efficiency of covert signaling}, $E_{cov}$. An overt signal reaches
$E_{ov} \times N$ agents and a covert signal reaches $E_{cov} \times N$ 
agents---which agents receive either signal type are chosen at random.
Overt signaling efficiency is set to $E_{ov}=0.5$ for all experiments presented
in the main text; (WE NEED TO RUN SENSITIVITY CHECKS ON THIS FOR THE SI). Covert
signaling efficiency is varied for one of our primary experimental variations
taking values from 0.1 to 0.5 in steps of 0.05.

\begin{itemize}
  \item The difference between overt and covert signals is the conditions
    under which the signal has an effect on the recieving agent's attitudes
    towards the sender.
    \begin{itemize}
      \item Overt signals, when recieved, always noticed and can change the
        receivers attitude about the signaler.
      \item Covert signals, when received, are not ``noticed'' by receivers
        if signaler and receiver are not sufficiently similar. 
      \item Recall agents are similar in our model if their inter-agent
    \end{itemize}
\end{itemize}

@@

Interaction occurs in two stages between two randomly-selected agents.
In the first stage, agents are matched in dyads at random. All agents
are matched with a partner. In the second stage, agents \emph{collaborate} with
one another depending on their attitudes towards one another and the homophily
level, $w$, in the experimental condition.
Recall that increased homophily means an increased 
preference for agents to only collaborate with similar others. 
This is operationalized in as
\begin{equation}
  \Pr(\text{$i$ collaborates with $j$}) = \frac{1 + w(a_{ij} + a_{ji})}{2}
  \label{eq:homophily}
\end{equation}
\noindent
where $w$ is the homophily value, constrained between 0 and 0.5, and $a_{ij}$
is agent $i$'s attitude towards agent $j$.
Note that as $w \rightarrow 0.5$, agents never collaborate with agents they 
dislike. Agents will only collaborate with agents they are neutral towards
or like. Furthermore, as $w \rightarrow 0.5$, agents more rarely are 
penalized for disliking their collaboration partner since they will never
interact with others whom they dislike.

@@

Agents gain payoffs when a dyad collaborates. Payoffs
are determined based on the similarity bonus, $s$, and the disliking
penalty $d$. The base payoff is 1, which is awarded if agents have neutral
attitudes towards one another, i.e., $a_{ij}=a_{ji}=1$. 
If the agents are similar, i.e.\ $s_{ij} > S$, then 
the payoff is supplemented by the similarity bonus, $s$. Note that the
collaboration penalty is not determined by \emph{dissimilarity}, but by
\emph{disliking}. Specifically, if just one agent dislikes the other, a penalty
of $d$ is subtracted from the base payoff. If both agents dislike one another,
a penalty of $2d$ is subtracted from the base payoff. 
In the SI we consider the case where the disliking penalty 
when both agents dislike each other is different from $d$. We call this $\delta$
and let it vary from 0 to $2d$. Note that, due to the orthogonality of 
similarity and attitude, it is possible for agents to be similar and 
to dislike one another. All possible payoffs are given in 
Table~\ref{tab:payoffs}.

\begin{table}[h]
  \vspace{1em}
  \centering
  \begin{tabular}{cccc}
    Similar? & $a_{ij}$ & $a_{ji}$ & Payoff \\
    \toprule
    \multirow{6}{*}{Yes}   & 1 & 1   & $1 + s$ \\
       & 1 & 0   & $1 + s$ \\
       & 1 & -1  & $1 + s - d$ \\
       & 0 & 0   & $1 + s$ \\
       & -1 & 0  & $1 + s - d$ \\
       & -1 & -1 & $1 + s - 2d$ \\

    % Yes   & 1 & 1   & $1 + s$ \\
    % Yes   & 1 & 0   & $1 + s$ \\
    % Yes   & 1 & -1  & $1 + s - d$ \\
    % Yes   & 0 & 0   & $1 + s$ \\
    % Yes   & -1 & 0  & $1 + s - d$ \\
    % Yes   & -1 & -1 & $1 + s - 2d$ \\
    \midrule
    % No    & 1 & -1  & $1 - d$ \\  <-- on further review, this seems impossible...
    %                                   since a_{ij}=1 is only possible if
    %                                   agents are similar.
    \multirow{3}{*}{No}    & 0 & 0   & $1$ \\
        & -1 & 0  & $1 - d$ \\
        & -1 & -1 & $1 - 2d$ \\
  \end{tabular}
  \caption{Interaction payoff matrix. Certain conditions are impossible, and so are not
  shown. For instance, it is necessary for two agents to be similar for 
  one agent to like another agent (i.e.\ have $a_{ij} = 1$). Note that
  due to churlish receiving, two agents may be similar, but one dislikes the
  other while the other likes the one. There could be agents who dislike one
  another due to churlish receiving if they have never signaled each other.}
  \label{tab:payoffs}
\end{table}

@@

First, we are interested in the prevalence of covert signaling in the
whole population at time
$t$, denoted $\rho_{cov,t}$. For a complete understanding of model dynamics,
we also track the prevalence of overt signaling and each receiving strategy,
denoted similarly (see Table~\ref{tab:outcomeMeasures}).
Usually, $t=T$, where $T$ is the number of iterations chosen for our 
computational experiments. The prevalence of overt signalers is the complement 
of the prevalence of covert signalers. One important result shows that the
prevalence of covert signalers at $t=T$ is positively correlated with the
prevalence of generous receivers at $t=T$. When considering $t=T$ we (SHOULD?)
drop the subscript and write $\rho_{cov}$, for example.

\begin{table}[H]
  \vspace{1em}
  \centering
  \begin{tabular}{rp{3in}} %p{5in}}
    Symbol & Measure \\ %& Description \\
    \toprule
      $\rho_{cov}$ & Prevalence of covert signalers\\
    $1 - \rho_{cov} = \rho_{ov}$ & Prevalence of overt signalers  \\
     $\rho_{gen}$ & Prevalence of generous receivers \\
    $1 - \rho_{gen} = \rho_{ch}$ & Prevalence of churlish receivers \\
    $\rho_s^{minor}$, $\rho_s^{maj}$ & Prevalence of strategy $s \in \{cov, ov, gen, ch\}$ amongst minority/majority \\
    $\Pr(\text{$s$ invades})$ & Probability strategy $s \in \{cov, ov, gen, ch\}$ invades 
  \end{tabular}
  \caption{Summary of outcome measures. To indicate any of these values at
  a particular time, we add an additional subscript. For example, $\rho_{cov,t}^{maj}$
  is the prevalence of covert signalers among the majority at time $t$.}
  \label{tab:outcomeMeasures}
\end{table}

In addition to the prevalence of signaling and receiving strategies in the whole
population, we need to track the prevalence of strategies within  
minority and majority populations, where the prevalence of siganling or
receiving strategy $s$ in the minority (majority) population at time $t$ is written
$\rho_{s,t}^{minor}$ ($\rho_{s,t}^{major}$). Again, we may drop $t$ when 
consider the long-time equilibrium ($t=T$) of these prevalence values.

Our final computational experiment analyzes whether strategy $s$ can ``invade''
the population and establish a stable, sizable population of agents adopting
that strategy. Here our outcome measure is the calculated probability (i.e.\
frequency) of invasion success, where a stable sizable population adopting
that strategy emerges. We write this $\Pr(\text{$s$ invades})$ where $s$
is covert, overt, generous, or churlish.

@@

This basic design initializes $N$ agents with a arndomized trait vector, 
an attitude vector, and a signaling and receiving strategy.
Randomly setting agent attributes means
choosing $\pm 1$ for each element of agent trait vectors with equal 
probabilities, and choosing a signaling and receiving strategy at random
with equal probabilities for each strategy type. Attributes are initialized
according to the agent's receiving strategy. Generous agents have all 
attitudes about other agents set to 0, indicating neutrality. Churlish agents
have all attitudes set to -1, since these agents dislike others by default.
This and all experiments iterate the model $T$ times, which
means $T$ signaling rounds, with $I$ interactions between signaling rounds,
and social learning after the signaling rounds. In this basic experiment,
we analyze the global prevalence of covert signalers at time $T$, denoted
$\rho_{cov,T}$, and the global prevalence of generous receivers at time $T$,
denoted $\rho_{gen,T}$, including calculating correlation between the two.

\subsubsection{Covert signaling in minority/majority populations}
The first variation on this basic model is intended to test our 
hypothesis that covert signaling prevalence in 
minority populations, denoted $\rho_{cov}^{minor}$, is inversely correlated with
homophily, $w$. For this, we initialize the first $M$ traits out of $K$ to mark the 
minority and majority populations. The minority population has its first
$M$ trait vector elements set to $+1$ and the majority population has its
first $M$ trait vector elements set to $-1$. For example, if $K=5$, $M=2$,
and agent $i$ is in the minority, then its trait vector would be
$\tau_i = (-1, -1, -1, \pm 1, \pm 1)$; if $i$ is in the majority, its 
trait vector would be $\tau_i = (1, 1, 1, \pm 1, \pm 1)$, where in the last
two positions the value is chosen randomly with equal probabilities.
In this experiment we analyze the prevalence of covert signalers and 
generous receivers in the minority and majority populations at time T: 
$\rho_{cov,T}^{minor}$, $\rho_{cov,T}^{major}$,
$\rho_{gen,T}^{minor}$, and $\rho_{gen,T}^{major}$.

@@

\subsection{Basic covert signaling prevalence dynamics}

% Here I co-vary the disliking penalties, which I set equal ($d=\delta$), and
% homophily, $w$. Here, $=0.25$ and $R=0.5$.

Our first task is to support our basic hypotheses that, other
things being equal, (1) covert signaling will
be the preferred strategy when penalties for disliking and 
being disliked is high and homophily is relatively weak; (2) increased homophily reduces the utility of
covert signaling since one rarely interacts when agents dislike one another;
and, finally, (3) if homophily is moderate or weak, increased covert signaling
efficiency leads to greater covert signaling prevalence.
To support these hypotheses, we present computational experiments below where
three explanatory parameters are varied systematically: homophily, $w$; 
disliking penalty, $d$; and covert signaling efficiency $E_{cov}$. 
Specifically, we co-vary homophily, disliking penalty, and covert signaling
efficiencies all in the same range $w,d,E_{cov} \in \{0.0, 0.05, 0.1, \ldots, 0.5\}$.
We co-vary these parameters in two separaete experiments. Both experiments
vary $w$ over those values. One experiment varies $d$ and one varies $E_{cov}$.

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/basic_disliking_signaling.pdf}
    \caption{Covert signaling prevalence under a variety of homophily and
    disliking penalty parameter values. }
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/basic_receptivity_signaling.pdf}
    \caption{Covert signaling prevalence under a variety of homophily and
    covert signaling efficiency values. $d=0.25$; all other parameters set to
  defaults listed in Table~}
  \end{subfigure}

  \caption{Covert signaling prevalence is sensitive to changes in all 
  three explanatory parameters for our basic experiment, homophily ($w$),
disliking penalty ($d$), and covert signaling efficiency ($E_{cov}$). 
In (a) $E_{cov}=0.25$; in (b) $d=0.25$. All other parameters in both sets of 
    results (a) and (b) are set to defaults listed in Table~\ref{tab:params}.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}

% \subsubsection{...as a function of covert signaling efficiency}

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/receptivity_allcombos_reg.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/disliking_allcombos_reg.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Correlation between proportion of covert signalers and proportion of
    churlish receivers for all tested parameter combinations in both 
    receptivity (a) and disliking (b) experiments. (NEED TO CHECK HOW I'M AVERAGING
    HERE AND POSSIBLY AGGREGATE FURTHER AS A SMOOTHING FILTER. ALSO NEED TO
). (THINK ABOUT HOW WE COULD USE PAIR PLOT GRIDS TO COMMUNICATE SOME OF
These, such as in https://jakevdp.github.io/PythonDataScienceHandbook/04.14-visualization-with-seaborn.html
I'm already going towards that with the invasion plots, but this would be
plotting correlations between outcome variables and maybe do a 2x2 with
signaling and receiving prevalences on x and y axes, respectively. Each plot
with be one of $s \in {cov, ov} \times {ch, gen}$.)}

  \label{fig:regressions}
\end{figure}

\subsubsection{Covert signaling is favored in less tolerant and more diverse societies}

(THIS PART REQUIRES NEW EXPERIMENTS. These need to be explained in Model 
  section. Below I am just writing a paragraph for myself to guide the 
experiment.)

Now we evaluate two related hypotheses, that (1) more tolerant societies
foster greater overt signaling prevalence and less covert signaling, i.e., more
tolerant societies promote honest communication; 
and (2) increased cultural diversity fosters increased 
covert signaling prevalence---that is, one must be more cautious since more
diversity means more social norms and taboos to navigate.

To test the first hypothesis that less tolerant societies foster greater
covert signaling prevalence, we
systematically varied the similarity threshold $S \in \{0.1, 0.2, \ldots, 0.9\}$.
Recall this threshold determines whether
two agents are deemed ``similar''. Two agents are similar if their similarity
$s_{ij} \geq S$ (see Equation~\ref{eq:similarity}; Table~\ref{tab:params}). 
We can think of the ``tolerance'' of agents to be $1-S$; then
high levels of tolerance mean a lower threshold for similarity.

\subsubsection{Covert signaling is favored among minority groups}

@@

We primarily vary the minority prevalence, $\rho^{minor} \in \{0.1, 0.15, \ldots, 0.45\}$. 
We vary $\rho^{minor}$ for two parameter pairs of $(K, M)$, where $K$ is the cultural 
complexity, and $M$ is the integer number of traits used to define 
majority/minority populations. The similarity threshold is set to $S=0.5$. 
We test the settings $K=3$, $M=1$, and $K=9$, $M=4$. We also test three
values of homophily and disliking penalty, representing low, medium, and high
levels for each: $w,d \in \{0.05, 0.25, 0.45\}$.

By setting $K$ and $M$ to these two values we test two different social
situations: in the first, $K=3$ and $M=1$, it is relatively easier for two binary traits
to match (1/4 probability) than the second case, 
with $K=9$ and $M=4$ where five binary traits must match (1/32 probability).
Our current results show \dots
Figure~\ref{fig:covert-signaling-minority-heatmap}.

@@

@@

In this experiment we begin with initial proportions, $\rho$ of one of the strategies
at 0.05 and consider this the ``invading'' strategy. $\rho_{cov,0}$ represents
the initial covert proportion, $\rho_{ov,0}$ the initial overt proportion,
$\rho_{ch,0}$ the initial churlish proportion, and $\rho_{gen,0}$ the 
initial generous proportion. We measure how often
a non-zero proportion of agents with the invading strategy manage to 
establish a permanent population, which we call invasion success. We calculated
invasion success for a number of experimental parameter settings, covarying
over disliking penalty ($d=\delta$) and homophily ($w$) in the first case,
and over relative covert receptivity ($r/R$) and homophily ($w$) 
in the second case (Figure~\ref{fig:cov-invades} below; Figures~\ref{fig:ov-invades} and~\ref{fig:ch-gen-invades} in the supplement).

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{Figures/covert_invades.pdf}
  % \caption{Covert invades, $\rho_{cov,0}=0.05$}
  \caption{Covert and overt sending strategy invasion success rates. 
    Lower homophily is more favorable for successful covert signaling invasion.
    This is due to lower homophily meaning agents cannot assort well into
    similar pairs prior to interaction.
    Similarly, greater homophily is more favorable for successful overt
    signaling invasion, where agents can better assort if they know each other's
    true traits. Unexpectedly, as covert receptivity increases, overt signaling
    is is more successful at invading and covert signaling is less successful
    at invading when the initial churlishness is high. When initial
    churlishness is small to moderate, the pattern is reversed.
  }
  \label{fig:cov-invades}
\end{figure}
